\section{ECG Timed Policies}
\label{sec:ecgPolicies}
A typical ECG cycle has three main wave (P, QRS-complex and T waves)~\cite{hampton2019ecg}. We will use following temporal features to define our policies - PR, QRS-complex, QT, RR and P-wave intervals.

The P-wave interval is captured by the duration between \emph{onset} of P-peak and the \emph{offset} of P-peak. It represents atrial depolarization. The QRS-complex is the combined duration of Q, R and S waves. It represents ventricular depolarization. The PR interval is the duration between \emph{onset} of P-wave and the \emph{onset} of QRS-complex. It represents the time taken by the electrical impulse to travel from the atria to the ventricles. The time it taken for the ventricular depolarization-repolarization cycle is marked by the QT interval. It is the duration from the \emph{onset} of QRS-complex to the \emph{offset} T-wave. The RR interval, the interval between two successive R-waves of the ECG, is the diagnostic tool for heart rate and heart rate variability measurement.

We consider the following ECG timed safety policies (combined policy) for
developing the proposed classifier and thereby monitoring the abnormalities in
the heart~\cite{hampton2019ecg}.

\begin{itemize}
	\item $\varphi_{ECG1}$: The PR interval in ECG should be in the range of 120-200 ms.
	
	\item $\varphi_{ECG2}$: The QRS-complex interval in ECG should be in the range of 80-120 ms.
	
	\item $\varphi_{ECG3}$: The QTc interval in ECG should be between 350-480 ms.
	
	\item $\varphi_{ECG4}$: The RR interval in ECG should be in the range of 600-1200 ms.
	
	\item $\varphi_{ECG5}$: The P-wave interval in ECG should be less than or equal to 120 ms.
	
\end{itemize}


%The policy $\varphi_{ECG}$ = $\varphi_{ECG1}$ $\cap$ $\varphi_{ECG2}$ $\cdots$ $\cap$ $\varphi_{ECG5}$ represents the all the policies. The policies are formalized as timed automata, and thereby runtime monitors are synthesized that monitor these policies and raise the alarm in case of violations.


%\begin{note}
	\textit{Note:} A healthy individual may not adhere to the standard ECG temporal specifications (timing ranges) all the time, however repeated violations of these policies can be an early indication of severe cardiac issues and thus need continuous monitoring. Details about how heart abnormalities are captured by ECG timed policies is discussed here~\cite{appendiz}	
%\end{note}


