\section{ECG Signal Processing}


\textit{ECG Dataset}: This work analyses the ECG records from the PTB-XL dataset \cite{wagner2020ptb}. The dataset consists of 21837 clinical 12-lead ECG records from 18885 patients, each of 10 seconds. It includes ECG from both men (52\%) and women (48\%) and spans the entire age range of 0 to 95 years. The collection includes a wide range of diagnostic classes, and cardiologists have annotated each ECG record. In this study, the policies are evaluated using lead II ECG readings (MLII).

%\textit{Preprocessing}: Generally, a raw ECG signal may be influenced by baseline wander, power line interference, noise, and artifacts. Hence, pre-processing of the signal is needed to filter unwanted data and extract vital information from the signals. We apply a band-pass Butterworth filter with 0.5 Hz and 40 Hz cutoff frequencies to remove baseline wander and noise from the input ECG signal.

\textit{Preprocessing}: Typically, a raw ECG signal can be distorted by several types of noise and artifacts. Hence, cleaning (preprocessing) the signal is therefore required to remove unnecessary data and obtain important information from the signals. To eliminate baseline wander and noise from the input ECG signal, a band-pass Butterworth filter with cutoff frequencies of 0.5 Hz and 40 Hz is employed.
%In this paper, the algorithm in [29] is used to bring the baseline drift to almost zero.

%\textit{Feature extraction}: After the filtering of the signal, the events of our interest are detected using the signal processing algorithm in python using the Neurokit2 tool \cite{makowski2021neurokit2}. The Pan-Tompkins algorithm \cite{pan1985real}) is used to detect the R-peak in the ECG signal. The other events such as $ \mathit{P_{onset}}, \mathit{P_{offset}}, \mathit{QRS_{onset}}, \mathit{QRS_{offset}}$ and $\mathit{T_{end}}  $ are extracted using discrete wavelet analysis implemented in Neurokit2 tool. 
%The \texttt{ECG\_Processing} module successfully detects all the relevant events for the recording. 
\textit{Feature extraction}: 
%Following the signal filtering, the events of our interest are found using the Neurokit2 tool's signal processing technique, which is implemented in Python. 
The R-peak in the ECG signal is located using the Pan-Tompkins technique \cite{pan1985real}) while we adapt the discrete wavelet analysis technique for extracting ECG events, such as $ \mathit{P_{onset}}, \mathit{P_{offset}}, \mathit{QRS_{onset}}, \mathit{QRS_{offset}}$ and $\mathit{T_{offset}} $ from an ECG signal.